README

### 2022-09-29 rmd/supporting_info.Rmd
rmd

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.")
```

>>>>

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge. Body size is categoraized as follows: total length (TL) $< 100$ mm (small), $100\\le$  TL $\\le 200$ (medium), and TL $> 200$ (large).")
```
